All the concepts behind TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages (Draft)

### 2020-11-27 article.tex
Paper TTT: agrego/curo una cita con su respectivo nombre de journal

\en{Humans develop complex skills because of an special integration of biological, cognitive and social processes~\citep{Koster2020}.}
\es{Los humanos desarrollan habilidades complejas gracias a una integraci\'on especial de los procesos biol\'ogicos, cognitivos y sociales~\citep{Koster2020}.}
\en{Our exceptional cognitive ability to imitate, combined with human long periods of juvenile dependency and postreproductive life span, allows us to learn things from others and transmit innovations through generations~\citep{citar}.}
\es{Nuestra extraordinaria capacidad para imitar, combinada con los largos períodos de aprendizaje juvenil y vida posreproductiva, permite a los humanos aprender de los dem\'as y transmitir las innovaci\'on a través de la generaciones~\citep{citar}.}
%
\en{As a population-based process, human adaptation is also affected by demographic characteristics, such as the size and structure of populations~\citep{Derex2020}.}
\es{Al ser un proceso poblacional, la adaptaci\'on humana también se ve afectada por caracter\'isticas demogr\'aficas, como el tama\~no y estructura de las poblaciones~\citep{Derex2020}.} 
% \en{Understanding the factors impacting in the positive or negative changes of skill could be used to develop new training strategies or adapting the environment to avoid unnecessary tasks.}
% \es{Hacer Conocer c\'omo cambian la habilidades de la personas en el tiempo es crucial en muchas \'areas.}

>>>>

\en{Humans develop complex skills because of an special integration of biological, cognitive and social processes~\citep{Koster2020}.}
\es{Los humanos desarrollan habilidades complejas gracias a una integraci\'on especial de los procesos biol\'ogicos, cognitivos y sociales~\citep{Koster2020}.}
\en{Our exceptional cognitive ability to imitate, combined with human long periods of juvenile dependency and postreproductive life span, allows us to learn things from others and transmit innovations through generations~\citep{Richerson2020}.}
\es{Nuestra extraordinaria capacidad para imitar, combinada con los largos períodos de aprendizaje juvenil y vida posreproductiva, permite a los humanos aprender de los dem\'as y transmitir las innovaci\'on a través de la generaciones~\citep{citar}.}
%
\en{As a population-based process, human adaptation is also affected by demographic characteristics, such as the size and structure of populations~\citep{Derex2020}.}
\es{Al ser un proceso poblacional, la adaptaci\'on humana también se ve afectada por caracter\'isticas demogr\'aficas, como el tama\~no y estructura de las poblaciones~\citep{Derex2020}.} 
% \en{Understanding the factors impacting in the positive or negative changes of skill could be used to develop new training strategies or adapting the environment to avoid unnecessary tasks.}
% \es{Hacer Conocer c\'omo cambian la habilidades de la personas en el tiempo es crucial en muchas \'areas.}
